sd_fig5

### 2020-07-06 examples/sd_fig5.Rmd
added code for plots

>>>>

```{r fig6, fig.align="center", fig.width=5, fig.height=3, cache=TRUE}
library(parallel)

optimal_h <- function (t) { sin(t)+cos(t) }

Df <- function (A,t) {
    exp(-t/(4*pi)) * ( h(t,A=A) - optimal_h(t) )^2
}

D <- function (A, upper=10, ...) {
    f <- function (t) { Df(A,t) }
    integrate(f, lower=0, upper=upper, ...)$value
}

get_F2s_nonunique <- function(tau1, tau2) {
    vc <- function(tau1, tau2, x, y) {
    out <- c(A_fn(tau1)[x,y], A_fn(tau2)[x,y])
    return(out)
}
mlist <- list()
count <- 1
for (i in 1:2) {
    for (j in 1:2) {
        for (k in 1:2)
            for (l in 1:2) {
                mlist[[count]] <- matrix(c(vc(tau1, tau2, 1, 1)[i], vc(tau1, tau2, 2, 1)[j], vc(tau1, tau2, 1, 2)[k], vc(tau1, tau2, 2, 2)[l]),2,2)
                count <- count + 1
            }
    }
}

f2list <- list()
count2 <- 1
for(i in 1:length(mlist)) {
    for (j in 1:length(mlist)) {
        f2list[[count2]] <- (mlist[[i]] + mlist[[j]])/2
        count2 <- count2 + 1
    }
}
return(f2list)
}

sys_gen_dist <- function(d) {
    sgd <- sqrt( sum( (A_fn(0) - A_fn(0+d))^2 ) )
    return(sgd)
}

dvec <- seq(0, 0.5, length.out=20)

D_F1 <- sapply(dvec, function (dtau) {
D(A=F1(tau1=0, tau2=0+dtau), upper = 10 )
} )

D_F2 <- do.call(cbind, mclapply(dvec, function (dtau) {
F2s <- get_F2s_nonunique(0, 0+dtau)
sapply(F2s, D, upper=10 )
}, mc.cores=detectCores() ) )

plot( sapply(dvec, sys_gen_dist), sqrt(D_F1), type='l', ylab="phenotype distance (D)", xlab="genetic distance", ylim=c(0, 2), lwd=3)
lines(sapply(dvec, sys_gen_dist), colMeans(sqrt(D_F2)), lty=1, type="l", ylim=c(0,2), col="steelblue4", lwd=3)
legend(0, 2, legend = c( expression(F[1]~"hybrids"), expression(F[2]~"hybrids")), lty=1, lwd=3, col=c("black", "steelblue4"))
